---
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(plotly)
library(flexdashboard)
```

## Motivation

The COVID-19 pandemic has drastically affected access to care across the United States due to such factors as diversion of medical resources and personnel, reduced access to transportation, and fear of transmission of COVID-19 in healthcare facilities. In addition to fears related to the pandemic,  public health measures in place to reduce its spread may cause an increase in mental health needs. The U.S. Census Bureau, the CDC, and four additional federal agencies have conducted the Household Pulse Survey to measure social and economic effects of the COVID-19 pandemic. Among these data are indicators of reduced access to care and depression/anxiety symptoms. 

## Initial Questions and Goal

We propose to investigate whether there exists a correlation between reduced access to care and depression/anxiety symptoms during COVID-19 using these data. We will compare reduction in access to care and mental health outcomes by age, gender, race, education and state.

## Related Work

## Data Source

Data was obtained from the Household Pulse Survey data which measures **indicators of anxiety or depression** (https://healthdata.gov/dataset/indicators-anxiety-or-depression-based-reported-frequency-symptoms-during-last-7-days) and **indicators of reduced access to care** (https://healthdata.gov/dataset/indicators-reduced-access-care-due-coronavirus-pandemic-during-last-4-weeks) during the coronavirus pandemic.

## Data Cleaning and Limitations

We combined two separate Household Pulse Survey datasets to be able to run comparisons on between indicators of anxiety or depression and indicators of reduced access to care.

```{r, message = FALSE, warning = FALSE}
mhealth_df =
  read_csv("data/Indicators_of_Anxiety_or_Depression_Based_on_Reported_Frequency_of_Symptoms_During_Last_7_Days.csv") %>%
  janitor::clean_names() %>% 
  rename(mhealth_ind = indicator,
         mhealth_value = value,
         mhealth_lowci = low_ci,
         mhealth_highci =  high_ci,
         mhealth_ci = confidence_interval,
         mhealth_qrange = quartile_range)

access_df =
  read_csv("data/Indicators_of_Reduced_Access_to_Care_Due_to_the_Coronavirus_Pandemic_During_Last_4_Weeks.csv") %>% 
  janitor::clean_names() %>% 
  rename(access_ind = indicator,
         access_value = value,
         access_lowci = low_ci,
         access_highci =  high_ci,
         access_ci = confidence_interval,
         access_qrange = quartile_range,
         time_period = week,
         time_period_label = week_label)


combined_df = 
  left_join(mhealth_df, access_df, by = c("phase", "group", "state", "subgroup", "time_period", "time_period_label"))  %>% 
  relocate("phase", "group", "state", "subgroup", "time_period", "time_period_label")
```

Our final dataset contains 10,881 observations and 18 variables:

* `phase`: Data  broken up into data collection phases
* `group`: Categories of data (gender, age, education, race, location)
* `state`: Location of data collection (national or specific states)
* `subgroup`: Group category broken up (i.e., gender is categorized by male and female)
* `time_period`: 2 week interval of data collection
* `time_period_label`: Label indicating specific dates of data collection
* `mhealth_ind`: Description of anxiety or depression indicator reported
* `mhealth_value`: Percent value of anxiety or depression indicator
* `mhealth_lowci`: Lower estimate of anxiety or depression confidence interval
* `mhealth_highci`: Upper estimate of anxiety or depression confidence interval
* `mhealth_ci`: Confidence interval of anxiety or depression value
* `mhealth_qrange`: Quartile range of anxiety or depression value
* `access_ind`: Description of access to health indicator reported
* `access_value`: Percent value of access to health indicator of each subgroup
* `access_lowci`: Lower estimate of access to health confidence interval
* `access_highci`: Upper estimate of access to health confidence interval
* `access_ci`: Confidence interval of access to health value
* `access_qrange`: Quartile range of access to health value

All values in this dataframe are averages

## Data Summary and Results

```{r, message = FALSE, warning = FALSE}
graph1_df =
  combined_df %>% 
  filter(mhealth_ind == "Symptoms of Anxiety Disorder or Depressive Disorder" & access_ind == "Delayed or Did Not Get Care, Last 4 Weeks" &  group == "By State") %>% 
  ggplot(aes(x = mhealth_value, y = access_value)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  labs(
    x = "Symptoms of Anxiety or Depressive Disorder (%)",
    y = "Delayed or Did Not Get Care in the Last 4 Weeks (%)",
    title = "Delayed or No Access to Care vs. Symptoms of Anxiety or Depression"
    )

graph2_df =
  combined_df %>% 
  filter(mhealth_ind == "Symptoms of Anxiety Disorder or Depressive Disorder" & access_ind == "Did Not Get Needed Care, Last 4 Weeks" &  group == "By State") %>% 
  ggplot(aes(x = mhealth_value, y = access_value)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  labs(
    x = "Symptoms of Anxiety or Depressive Disorder (%)",
    y = "Did Not Get Needed Care in the Last 4 Weeks (%)",
    title = "No Access to Care vs. Symptoms of Anxiety or Depression"
    )

graph3_df =
  combined_df %>% 
  filter(mhealth_ind == "Symptoms of Anxiety Disorder or Depressive Disorder" & access_ind == "Delayed Medical Care, Last 4 Weeks" &  group == "By State") %>% 
  ggplot(aes(x = mhealth_value, y = access_value)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  labs(
    x = "Symptoms of Anxiety or Depressive Disorder (%)",
    y = "Delayed Medical Care in the Last 4 Weeks (%)",
    title = "Delayed Access to Care vs. Symptoms of Anxiety or Depression"
    )
```

## Interactive Plots

## Discussion
 