---
title: "shiny_test"
author: "Joana Petrescu"
date: "11/30/2020"
output: html_document
---

## Load packages

```{r}

#install.packages("shiny")
library(shiny)
#install.packages("leaflet")
library(leaflet)
#install.packages("maps")
library(maps)

```

## Shiny components

Two components for every app:
1. user interface (html)
2. server instructions (R)

### Template for every Shiny app

```{r}

ui <- fluidPage()

server <- function(input, output) {}

shinyApp(ui = ui, server = server)

```

## Inputs and Outputs

inputs = things user can toggle
outputs = R objects user sees, respond to changes in input (plots, tables, text)

### Input types

allow for user interaction

```{r}

## buttons
actionButton()
submitButton()

## checkboxes
## potentially include/exclude states
checkboxInput()
checkboxGroupInput()

## radio buttons
radioButtons()

## select box
## toggle between gender, race, education, etc.
selectInput()

## sliders
## select time frame
sliderInput()

## syntax
sliderInput(inputId = "num", label = "Choose a number", ...)

```

### Outputs

plots, tables, text

```{r}

## interactive table
dataTableOutput()

## plot
plotOutput()

## regular table
tableOutput()

## Shiny UI element
uiOutput()

## syntax
plotOutput(outputId = "hist")

```

this holds space for output plot but you need to provide instructions for building plot in server function

### Server function

instructions for building outputs from inputs

1. save objects to display in ui to `output$`

`output$hist` in server function builds `plotOutput("hist)`

2. what you save to output is something you build with `render*()` function

these correspond to outputs in ui (eg. `renderDataTable()`, `renderPlot()`, `renderTable()`, `renderUI()`)

3. use input values w/ `input$` when you want them to be interactive

```{r}

## syntax
server <-  function(input, output) {
  output$hist <- renderPlot({
    title <- "input$num random normal values"
    hist(rnorm(input$num), main = title) 
    })
}

```

### Saving

Save script that ends with shinyApp() as `app.R` in *own directory*

Include all datasets, images, etc. in directory

### Sharing

`Shinyapps.io` server

Make account

Devtools install `shinyapps` from github

Link R-studio to `shinyapps.io` account

Makes URL for app

### Reactive function

code chunk that bulids/rebuilds an object **in response to** set of reactive values (controlled in ui)

```{r}

## render functions build objects displayed in app, rebuild when input changes
render*()

## build a reactive object (function) that can be used to make multiple display objects (plot, table) respond to the same input
## caches values of input
## is a function, call w/ parentheses
reactive()

## makes non-reactive object, updated only when another input is updated for same object (eg. prevent title from updating faster than typing)
isolate()

## action button triggers function
observeEvent(input$clicks, { print(input$clicks) })
observe({ print(input$clicks) })

## delay input update until you click action button ("update" button)
eventReactive(input$go, { rnorm(input$num) })

## create list of reactive values independent of user input
## can be used w/ observeEvent to create button that overwrites user input value (reset, etc.)
reactiveValues(data = rnorm(100))

```

any code that appears in server function will be run every time a user interacts w/ app

any code that only needs to be run once (eg. load libraries) put outside of server function to be run once per session

### User interface

HTML ui

Shiny has tags that translate from R to HTML: https://shiny.rstudio.com/articles/tag-glossary.html

images must be in *www* subdirectory

### Layout

grid organization

```{r}

## add rows w/ fluidRow, each row has 12 units, call columns w/ width (out of 12) and offset within row
ui <- fluidPage(
  
  fluidRow(
    column(3, sliderInput()),
    column(5)
  ),
  fluidRow(
    column(4, offset = 8, plotOutput("hist"))
  )
  
)

```

join components together into panels w/ `wellPanel()`

for layering/stacking panels

```{r}

## create stackable layer of elements, first argument is title
## combine w/ one of the following functions
tabPanel("Tab 1", ...)

## pass tabPanels through it to layer tabPanels, toggle between them w/ tabs
## creates a navigation section (tabs) and content section
tabsestPanel()

## pass tabPanels through it to create sidebar of links to navigate between tabs
navlistPanel()

```

there are preset layouts:
https://shiny.rstudio.com/articles/layout-guide.html

## Leaflet + Shiny to make apps

call `leafletOutput` in ui, `renderLeaflet` in server to create Leaflet map object

https://rstudio.github.io/leaflet/

## Read data

```{r}
mhealth_df =
  read_csv("data/Indicators_of_Anxiety_or_Depression_Based_on_Reported_Frequency_of_Symptoms_During_Last_7_Days.csv") %>%
  janitor::clean_names() %>% 
  rename(mhealth_ind = indicator,
         mhealth_value = value,
         mhealth_lowci = low_ci,
         mhealth_highci =  high_ci,
         mhealth_ci = confidence_interval,
         mhealth_qrange = quartile_range)

access_df =
  read_csv("data/Indicators_of_Reduced_Access_to_Care_Due_to_the_Coronavirus_Pandemic_During_Last_4_Weeks.csv") %>% 
  janitor::clean_names() %>% 
  rename(access_ind = indicator,
         access_value = value,
         access_lowci = low_ci,
         access_highci =  high_ci,
         access_ci = confidence_interval,
         access_qrange = quartile_range,
         time_period = week,
         time_period_label = week_label)

combined_df = 
  left_join(mhealth_df, access_df, by = c("phase", "group", "state", "subgroup", "time_period", "time_period_label")) %>% 
  relocate("phase", "group", "state", "subgroup", "time_period", "time_period_label")

```

## Plot state data

```{r}

coordinates <- as.data.frame(state.carto.center) %>% mutate(state = state.name)

mhealth_test <- mhealth_df %>% filter(group == "By State") %>% filter(mhealth_ind == "Symptoms of Anxiety Disorder or Depressive Disorder") %>% arrange(state) %>% merge(coordinates, by = "state")

states = map("state", fill = TRUE, plot = FALSE)

leaflet(states) %>%
  addTiles() %>%
  addPolygons()


```

