---
title: "shiny_test"
author: "Joana Petrescu"
date: "11/30/2020"
output: html_document
---

## Load packages

```{r}

library(tidyverse)
#install.packages("shiny")
library(shiny)
#install.packages("leaflet")
library(leaflet)
#install.packages("geojsonio")
library(geojsonio)

```

## Shiny components

Two components for every app:
1. user interface (html)
2. server instructions (R)

### Template for every Shiny app

```{r}

ui <- fluidPage()

server <- function(input, output) {}

shinyApp(ui = ui, server = server)

```

## Inputs and Outputs

inputs = things user can toggle
outputs = R objects user sees, respond to changes in input (plots, tables, text)

### Input types

allow for user interaction

```{r}

## buttons
actionButton()
submitButton()

## checkboxes
## potentially include/exclude states
checkboxInput()
checkboxGroupInput()

## radio buttons
radioButtons()

## select box
## toggle between gender, race, education, etc.
selectInput()

## sliders
## select time frame
sliderInput()

## syntax
sliderInput(inputId = "num", label = "Choose a number", ...)

```

### Outputs

plots, tables, text

```{r}

## interactive table
dataTableOutput()

## plot
plotOutput()

## regular table
tableOutput()

## Shiny UI element
uiOutput()

## syntax
plotOutput(outputId = "hist")

```

this holds space for output plot but you need to provide instructions for building plot in server function

### Server function

instructions for building outputs from inputs

1. save objects to display in ui to `output$`

`output$hist` in server function builds `plotOutput("hist)`

2. what you save to output is something you build with `render*()` function

these correspond to outputs in ui (eg. `renderDataTable()`, `renderPlot()`, `renderTable()`, `renderUI()`)

3. use input values w/ `input$` when you want them to be interactive

```{r}

## syntax
server <-  function(input, output) {
  output$hist <- renderPlot({
    title <- "input$num random normal values"
    hist(rnorm(input$num), main = title) 
    })
}

```

### Saving

Save script that ends with shinyApp() as `app.R` in *own directory*

Include all datasets, images, etc. in directory

### Sharing

`Shinyapps.io` server

Make account

Devtools install `shinyapps` from github

Link R-studio to `shinyapps.io` account

Makes URL for app

### Reactive function

code chunk that bulids/rebuilds an object **in response to** set of reactive values (controlled in ui)

```{r}

## render functions build objects displayed in app, rebuild when input changes
render()

## build a reactive object (function) that can be used to make multiple display objects (plot, table) respond to the same input
## caches values of input
## is a function, call w/ parentheses
reactive()

## makes non-reactive object, updated only when another input is updated for same object (eg. prevent title from updating faster than typing)
isolate()

## action button triggers function
observeEvent(input$clicks, { print(input$clicks) })
observe({ print(input$clicks) })

## delay input update until you click action button ("update" button)
eventReactive(input$go, { rnorm(input$num) })

## create list of reactive values independent of user input
## can be used w/ observeEvent to create button that overwrites user input value (reset, etc.)
reactiveValues(data = rnorm(100))

```

any code that appears in server function will be run every time a user interacts w/ app

any code that only needs to be run once (eg. load libraries) put outside of server function to be run once per session

### User interface

HTML ui

Shiny has tags that translate from R to HTML: https://shiny.rstudio.com/articles/tag-glossary.html

images must be in *www* subdirectory

### Layout

grid organization

```{r}

## add rows w/ fluidRow, each row has 12 units, call columns w/ width (out of 12) and offset within row
ui <- fluidPage(
  
  fluidRow(
    column(3, sliderInput()),
    column(5)
  ),
  fluidRow(
    column(4, offset = 8, plotOutput("hist"))
  )
  
)

```

join components together into panels w/ `wellPanel()`

for layering/stacking panels

```{r}

## create stackable layer of elements, first argument is title
## combine w/ one of the following functions
tabPanel("Tab 1", ...)

## pass tabPanels through it to layer tabPanels, toggle between them w/ tabs
## creates a navigation section (tabs) and content section
tabsestPanel()

## pass tabPanels through it to create sidebar of links to navigate between tabs
navlistPanel()

```

there are preset layouts:
https://shiny.rstudio.com/articles/layout-guide.html

## Leaflet + Shiny to make apps

call `leafletOutput` in ui, `renderLeaflet` in server to create Leaflet map object

https://rstudio.github.io/leaflet/

## Read data

```{r}
mhealth_df =
  read_csv("data/Indicators_of_Anxiety_or_Depression_Based_on_Reported_Frequency_of_Symptoms_During_Last_7_Days.csv") %>%
  janitor::clean_names() %>% 
  rename(mhealth_ind = indicator,
         mhealth_value = value,
         mhealth_lowci = low_ci,
         mhealth_highci =  high_ci,
         mhealth_ci = confidence_interval,
         mhealth_qrange = quartile_range)

access_df =
  read_csv("data/Indicators_of_Reduced_Access_to_Care_Due_to_the_Coronavirus_Pandemic_During_Last_4_Weeks.csv") %>% 
  janitor::clean_names() %>% 
  rename(access_ind = indicator,
         access_value = value,
         access_lowci = low_ci,
         access_highci =  high_ci,
         access_ci = confidence_interval,
         access_qrange = quartile_range,
         time_period = week,
         time_period_label = week_label)

combined_df = 
  left_join(mhealth_df, access_df, by = c("phase", "group", "state", "subgroup", "time_period", "time_period_label")) %>% 
  relocate("phase", "group", "state", "subgroup", "time_period", "time_period_label")

mhealth_date <- mhealth_df %>% 
  filter(group == "By State", mhealth_ind == "Symptoms of Anxiety Disorder or Depressive Disorder")  %>% 
  separate(time_period_label, c("first_date", "second_date"), sep = " - ") %>%
  separate(second_date, c("month", "day"), sep = " ") %>%
  mutate(year = 2020) %>%
  mutate(second_date = paste(year, month, day, sep="-") %>% ymd() %>% as.Date()) %>%
  select(mhealth_ind, state, second_date, mhealth_value, mhealth_ci)

```

## Make choropleth of mental health indicator values for each sstate

```{r}

## import .json file w/ state spatial polygons
states <- geojson_read(x = "https://raw.githubusercontent.com/PublicaMundi/MappingAPI/master/data/geojson/us-states.json", what = "sp")

class(states) 

## simplify mental health data
mhealth_test <- mhealth_df %>% filter(group == "By State", time_period == 16, mhealth_ind == "Symptoms of Anxiety Disorder or Depressive Disorder")

## make color palette
pal <- colorNumeric(
  palette = "Blues",
  domain = mhealth_test$mhealth_value)

## add state shape polygons to US map
leaflet(mhealth_test) %>% 
  addPolygons(data = states, fillOpacity = 1, color = ~pal(mhealth_test$mhealth_value), stroke = FALSE, smoothFactor = 0.2)

```

## Shiny interaction w/ map

```{r}

## import US states .json file
states <- geojson_read(x = "https://raw.githubusercontent.com/PublicaMundi/MappingAPI/master/data/geojson/us-states.json", what = "sp")

mhealth_map <- mhealth_df %>% 
  filter(group == "By State", mhealth_ind == "Symptoms of Anxiety Disorder or Depressive Disorder")

access_map <-  access_df %>% 
  filter(group == "By State", access_ind == "Delayed or Did Not Get Care, Last 4 Weeks")

pal <- colorNumeric(
  palette = "Blues",
  domain = mhealth_map$mhealth_value)

pal2 <- colorNumeric(
  palette = "Greens",
  domain = access_map$access_value)

week_labels <- mhealth_map %>% select(time_period_label) %>% unique


## set up shiny ui

ui <- fluidPage(
  

  wellPanel(
  sliderInput("week", "Survey time period:", min = 1, max = 17, value = 1),

  textOutput("week_label")
  ),
  
  fluidRow(
  column(6, leafletOutput("mh_map")),
  
  column(6, leafletOutput("access_map"))
  ),
  
  img(src = "coronavirus_cases.png")
  
)

## set up shiny server

server <- function(input, output) {
  
  
  mhealth_updated <- reactive({ mhealth_map %>% filter(time_period == input$week) })
  
  output$week_label <- renderText({
   paste(week_labels[input$week,])

  })

  output$mh_map <- renderLeaflet({
    leaflet(mhealth_updated()) %>% 
      addPolygons(
        data = states, 
        fillOpacity = 1, 
        color = ~pal(mhealth_updated()$mhealth_value), 
        stroke = FALSE, 
        smoothFactor = 0.2,
        label = paste(mhealth_updated()$state, mhealth_updated()$mhealth_value),
        labelOptions = labelOptions(
          style = list("font-weight" = "normal", padding = "3px 8px"),
          textsize = "15px",
          direction = "auto")) %>%
      
      addLegend(
        pal = pal,
        values = ~mhealth_map$mhealth_value,
        opacity = 0.7,
        title = "% MH symptoms",
        position = "bottomright") 
  })
  
    access_updated <- reactive({ access_map %>% filter(time_period == input$week) })

  output$access_map <- renderLeaflet({
    leaflet(access_updated()) %>% 
      addPolygons(
        data = states, 
        fillOpacity = 1, 
        color = ~pal2(access_updated()$access_value), 
        stroke = FALSE, 
        smoothFactor = 0.2,
        label = paste(access_updated()$state, access_updated()$access_value),
        labelOptions = labelOptions(
          style = list("font-weight" = "normal", padding = "3px 8px"),
          textsize = "15px",
          direction = "auto")) %>%
      
      addLegend(
        pal = pal2,
        values = ~access_map$access_value,
        opacity = 0.7,
        title = "% reduced access",
        position = "bottomright") 
  })
  
}

shinyApp(ui, server)


```

