---
title: "shiny_test"
author: "Joana Petrescu"
date: "11/30/2020"
output: html_document
---

## Load packages

```{r}

#install.packages("shiny")
library(shiny)
#install.packages("leaflet")
library(leaflet)

```

## Shiny components

Two components for every app:
1. user interface (html)
2. server instructions (R)

### Template for every Shiny app

```{r}

ui <- fluidPage()

server <- function(input, output) {}

shinyApp(ui = ui, server = server)

```

## Inputs and Outputs

inputs = things user can toggle
outputs = R objects user sees, respond to changes in input (plots, tables, text)

### Input types

allow for user interaction

```{r}

## buttons
actionButton()
submitButton()

## checkboxes
## potentially include/exclude states
checkboxInput()
checkboxGroupInput()

## radio buttons
radioButtons()

## select box
## toggle between gender, race, education, etc.
selectInput()

## sliders
## select time frame
sliderInput()

## syntax
sliderInput(inputId = "num", label = "Choose a number", ...)

```

### Outputs

plots, tables, text

```{r}

## interactive table
dataTableOutput()

## plot
plotOutput()

## regular table
tableOutput()

## Shiny UI element
uiOutput()

## syntax
plotOutput(outputId = "hist")

```

this holds space for output plot but you need to provide instructions for building plot in server function

### Server function

instructions for building outputs from inputs

1. save objects to display in ui to `output$`

`output$hist` in server function builds `plotOutput("hist)`

2. what you save to output is something you build with `render*()` function

these correspond to outputs in ui (eg. `renderDataTable()`, `renderPlot()`, `renderTable()`, `renderUI()`)

3. use input values w/ `input$` when you want them to be interactive

```{r}

## syntax
server <-  function(input, output) {
  output$hist <- renderPlot({
    title <- "num random normal values"
    hist(rnorm(input$num), main = title) 
    })
}

```




## Read data

```{r}
mhealth_df =
  read_csv("data/Indicators_of_Anxiety_or_Depression_Based_on_Reported_Frequency_of_Symptoms_During_Last_7_Days.csv") %>%
  janitor::clean_names() %>% 
  rename(mhealth_ind = indicator,
         mhealth_value = value,
         mhealth_lowci = low_ci,
         mhealth_highci =  high_ci,
         mhealth_ci = confidence_interval,
         mhealth_qrange = quartile_range)

access_df =
  read_csv("data/Indicators_of_Reduced_Access_to_Care_Due_to_the_Coronavirus_Pandemic_During_Last_4_Weeks.csv") %>% 
  janitor::clean_names() %>% 
  rename(access_ind = indicator,
         access_value = value,
         access_lowci = low_ci,
         access_highci =  high_ci,
         access_ci = confidence_interval,
         access_qrange = quartile_range,
         time_period = week,
         time_period_label = week_label)

combined_df = 
  left_join(mhealth_df, access_df, by = c("phase", "group", "state", "subgroup", "time_period", "time_period_label")) %>% 
  relocate("phase", "group", "state", "subgroup", "time_period", "time_period_label")

```

